The relativistic capture of compact objects by intermediate-mass black holes

### 2019-04-19 article.tex
Converted to MNRAS style, the file is now mn tex

\shorttitle{IMRIs in GCs}
\shortauthors{Arca Sedda, M. and Amaro-Seoane, P.}

@@

\title{Intermediate mass ratio formation in globular clusters: perspectives for LISA sources formation}

@@

\author{Manuel Arca Sedda and Pau Amaro-Seoane}
\affil{Zentrum f\"{u}r Astronomie der Universit\"{a}t  Heidelberg\\
Astronomisches Rechen-Institut\\
M\"onchhofstrasse 12-14\\
Heidelberg, D-69120, DE}
\affil{...}

\begin{abstract}
We study the formation and evolution of intermediate mass ratio inspirals (IMRIs) triggered by the interactions between stellar black holes and an intermediate black hole (IMBH) inhabiting. We show the probability for an IMRI to form is an increasing function of the IMBH mass, representing a viable channel for the development of gravitational wave sources that can be possibly observed with the future generation of detectors.
\end{abstract}

@@

Sonderforschungsbereich SFB 881 "The Milky Way System" (subproject Z2) of the German Research Foundation (DFG) for the financial support provided. This work benefited of financial support from the Alexander von Humboldt Foundation, which granted MAS research program ``The evolution of black holes from stellar to galactic scales''. 
This work benefited from support by the ISSI (Bern), through its Intern. Team prog. ref. no. 393 {\it The Evolution of Rich Stellar Populations \& BH Binaries} (2017-18).

\footnotesize{
\bibliographystyle{mn2e}
\bibliography{ASetal2015}
}

>>>>

\shorttitle{Formation of IMRIs}
\shortauthors{Arca Sedda, M. and Amaro-Seoane, P.}

@@

\title{Formation and evolution of intermediate-mass ratio inspirals}

@@

\author{Manuel Arca Sedda and Pau Amaro-Seoane}
\affil{Zentrum f\"{u}r Astronomie der Universit\"{a}t  Heidelberg\\
Astronomisches Rechen-Institut\\
M\"onchhofstrasse 12-14\\
Heidelberg, D-69120, DE}
\affil{
Institute of Space Sciences (ICE, CSIC) \& Institut d'Estudis Espacials de Catalunya (IEEC)\\
at Campus UAB, Carrer de Can Magrans s/n 08193 Barcelona, Spain\\
Institute of Applied Mathematics, Academy of Mathematics and Systems Science, CAS, Beijing 100190, China\\
Kavli Institute for Astronomy and Astrophysics, Beijing 100871, China\\
Zentrum f{\"u}r Astronomie und Astrophysik, TU Berlin, Hardenbergstra{\ss}e 36, 10623 Berlin, Germany
}

\begin{abstract}
%
% Motivation: Why do we care about the problem and the results?
% ==============================================================
%

%
% Problem statement: What problem are we trying to solve?
% ========================================================
%

%
% Approach: How did we go about solving or making progress on the problem?
% =========================================================================
%

%
% Results: What's the answer?
% ===========================
%

%
% Conclusions: What are the implications of our answer?
% ======================================================
%
We study the formation and evolution of intermediate mass ratio inspirals (IMRIs) triggered by the interactions between stellar black holes and an intermediate black hole (IMBH) inhabiting. We show the probability for an IMRI to form is an increasing function of the IMBH mass, representing a viable channel for the development of gravitational wave sources that can be possibly observed with the future generation of detectors.
\end{abstract}

@@

Sonderforschungsbereich SFB 881 "The Milky Way System" (subproject Z2) of the
German Research Foundation (DFG) for the financial support provided. This work
benefited of financial support from the Alexander von Humboldt Foundation,
which granted MAS research program ``The evolution of black holes from stellar
to galactic scales''.  This work benefited from support by the ISSI (Bern),
through its Intern. Team prog. ref. no. 393 {\it The Evolution of Rich Stellar
Populations \& BH Binaries} (2017-18).  PAS acknowledges support from the
Ram{\'o}n y Cajal Programme of the Ministry of Economy, Industry and
Competitiveness of Spain, as well as the COST Action GWverse CA16104. This work
was supported by the National Key R\&D Program of China (2016YFA0400702) and
the National Science Foundation of China (11721303).

\footnotesize{
\bibliographystyle{mn2e}
\bibliography{aamnem99,biblio,ASetal2015}
}

### 2019-04-19 mn.tex
Converted to MNRAS style, the file is now mn tex

\documentclass[twocolumn]{aastex62}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{color}
\usepackage{appendix}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}

@@

\graphicspath{{./}{./}}

\received{}
\revised{revised to \today}
\accepted{}

\submitjournal{ApJ (not yet ..)}

\shorttitle{Formation of IMRIs}
\shortauthors{Arca Sedda, M. and Amaro-Seoane, P.}

@@

\title{Formation and evolution of intermediate-mass ratio inspirals}

\correspondingauthor{Manuel Arca Sedda}
\email{m.arcasedda@gmail.com}

\author{Manuel Arca Sedda and Pau Amaro-Seoane}
\affil{Zentrum f\"{u}r Astronomie der Universit\"{a}t  Heidelberg\\
Astronomisches Rechen-Institut\\
M\"onchhofstrasse 12-14\\
Heidelberg, D-69120, DE}
\affil{
Institute of Space Sciences (ICE, CSIC) \& Institut d'Estudis Espacials de Catalunya (IEEC)\\
at Campus UAB, Carrer de Can Magrans s/n 08193 Barcelona, Spain\\
Institute of Applied Mathematics, Academy of Mathematics and Systems Science, CAS, Beijing 100190, China\\
Kavli Institute for Astronomy and Astrophysics, Beijing 100871, China\\
Zentrum f{\"u}r Astronomie und Astrophysik, TU Berlin, Hardenbergstra{\ss}e 36, 10623 Berlin, Germany
}

@@

%
% Conclusions: What are the implications of our answer?
% ======================================================
%
We study the formation and evolution of intermediate mass ratio inspirals (IMRIs) triggered by the interactions between stellar black holes and an intermediate black hole (IMBH) inhabiting. We show the probability for an IMRI to form is an increasing function of the IMBH mass, representing a viable channel for the development of gravitational wave sources that can be possibly observed with the future generation of detectors.
\end{abstract}

\keywords{black holes - supermassive black holes - galactic nuclei - gravitational waves}

@@

\section*{Acknowledgements}

Sonderforschungsbereich SFB 881 "The Milky Way System" (subproject Z2) of the
German Research Foundation (DFG) for the financial support provided. This work
benefited of financial support from the Alexander von Humboldt Foundation,
which granted MAS research program ``The evolution of black holes from stellar
to galactic scales''.  This work benefited from support by the ISSI (Bern),
through its Intern. Team prog. ref. no. 393 {\it The Evolution of Rich Stellar
Populations \& BH Binaries} (2017-18).  PAS acknowledges support from the
Ram{\'o}n y Cajal Programme of the Ministry of Economy, Industry and
Competitiveness of Spain, as well as the COST Action GWverse CA16104. This work
was supported by the National Key R\&D Program of China (2016YFA0400702) and
the National Science Foundation of China (11721303).

\footnotesize{
\bibliographystyle{mn2e}
\bibliography{aamnem99,biblio,ASetal2015}
}

\end{document}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{epsfig,graphicx,latexsym,amsmath,amssymb}
\usepackage[export]{adjustbox}[2011/08/13]
% Centers the content in the given length
% Use as:
% \includegraphics[width=1.2\textwidth,center]{image}

\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathrsfs}
\usepackage{lastpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{draftwatermark}          %
%\SetWatermarkText{Do not circulate}  %
%\SetWatermarkLightness{0.8}          %
%\SetWatermarkScale{0.7}              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{color}

@@

\newcommand{\pau}[1]{\textcolor{cyan}{{\bf Comment from Pau:} ``#1.''}}

\bibpunct[,]{(}{)}{;}{a}{}{,}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Formation of intermediate-mass ratio inspirals]
      {The relativistic capture of compact objects by intermediate-mass black holes}

\author[M. Arca Sedda \& P. Amaro-Seoane] % Running authors, % use abbrev. names here
{
Manuel Arca Sedda$^{1}$
                        \thanks{E-mail: m.arcasedda@gmail.com (MAS)} \&
Pau Amaro-Seoane$^{2}$
                        \thanks{E-mail: pau@ice.cat (PAS)},
                                % Thanks goes to 1rst author only
                                % Continue with other authors, full names
   \\
                                % Now addresses come
                                % Separate with \\ but for
                                % the last one
$^{1}$Zentrum f\"{u}r Astronomie, Astronomisches Rechen-Institut, M\"onchhofstrasse 12-14, Heidelberg, D-69120, Germany\\
$^{2}$Institut de Ci{\`e}ncies de l'Espai (CSIC-IEEC) at Campus UAB,
Carrer de Can Magrans s/n 08193 Barcelona, Spain\\
Institute of Applied Mathematics, Academy of Mathematics and Systems Science,
CAS, Beijing 100190, China\\
Kavli Institute for Astronomy and Astrophysics, Beijing 100871, China\\
Zentrum f{\"u}r Astronomie und Astrophysik, TU Berlin, Hardenbergstra{\ss}e 36,
10623 Berlin, Germany
}

@@

\date{draft \today}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{}

\maketitle

\label{firstpage}

@@

%
% Conclusions: What are the implications of our answer?
% ======================================================
%
\end{abstract}

\begin{keywords}
% Llista sencera: http://oxfordjournals.org/our_journals/mnrasl/for_authors/mnraskey.pdf
a keyword -- another.
\end{keywords}

@@

\section*{Acknowledgments}

MAS thanks the Sonderforschungsbereich SFB 881 ``The Milky Way System''
(subproject Z2) of the German Research Foundation (DFG) for the financial
support provided. This work benefited of financial support from the Alexander
von Humboldt Foundation, which granted MAS' research program ``The evolution of
black holes from stellar to galactic scales''.  This work benefited from
support by the ISSI (Bern), through its Intern. Team prog. ref. no. 393 {\it
The Evolution of Rich Stellar Populations \& BH Binaries} (2017-18).  PAS
acknowledges support from the Ram{\'o}n y Cajal Programme of the Ministry of
Economy, Industry and Competitiveness of Spain, as well as the COST Action
GWverse CA16104. This work was supported by the National Key R\&D Program of
China (2016YFA0400702) and the National Science Foundation of China (11721303).
PAS is indebted with the Edoardo Amaldi Center at La Sapienza University in
Rome for two visits in 2019.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{mn}            %
\bibliography{aamnem99,biblio,ASetal2015}    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{LastPage}
\end{document}
